Objectification in Action: Self- and Other-Objectification in Same-gender Interactions

### 2020-07-27 Final_Manuscript.tex
fixed reference

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
            pdfauthor={Randi L. Garcia, Kat Kyuchukova, \& Asha Hinson},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Objectification in Action: Self- and Other-Objectification in
Same-gender Interactions}
    \author{Randi L. Garcia\textsuperscript{1, 2}, Kat
Kyuchukova\textsuperscript{1}, \& Asha Hinson\textsuperscript{1}}
    \date{}

@@

OUTLINE - Introduction: Objectification theory says stuff. Recently
we've learned about interpersonal objectification but we only know it
about mixed gender. We know women objectify each other, but what about
in interpersonal interactions? - Self-objectification - SSO versus TSO -
Does this process of self-objectification also lead women to objectify
other women? - Women objectifying other women - Lots of evidence, but we
don't know if this happens interpersonally - Interpersonal
objectifcation research is a whole thing now, but there are no studies
(or theoretical models) that include women-on-women interpersonal
objectification processes. - Relationships and objectification - Both
romantic relationships and relationships in general have been studies in
the context of objectification, but neither of these literatures have
investigated specifically same-gender relationships. - Authenticity
paragraph? - Current Study - Alternative predictions

Roberts and Fredrickson (1997)\enquote{s Objectification Theory,
suggests that women are objectified in interpersonal encounters, and
that the effect might be strongest from men, but possibly also from
women. Psychological researchers studying the sexual objectification of
women, and the resulting self-objectification that follows, have in
recent years explored the interpersonal process of the objectification -
self-objectification link. For exmaple, in a face-to-face mixed-gender
dyadic study, Garcia, Earnshaw, and Quinn (2016) found that men's
reported objectificaiton of their female interaction partner during an
interaction was associated with increased sefl-objectification reported
by their partner. Gervais, Sáez, Riemer, and Klein (2020) has reviewed
the literature on interpersonal self-objectification and has organized
the the process in a theoretical model called the SIMO, but this model
is only relevant for mixed-gender encouters. Although there is ample
evidence that women objectify other women (Loughnan et al., 2015a; Puvia
\& Vaes, 2013), there is currently no studies investigating the process
of interpersonal objectification same-gender interactions. Does
objectification by a female interaction partner have the same downstream
negative consequences as being objectified by a male interaction
partner? For example, perhaps women could be amplifying each others}
self-objectification as they get ready to go out for the night,
\emph{before} the theoretical encounters with men outlined in Gervais et
al. (2020) occur.

Self-objectification is a multidimensional process that accounts for the
cognitive mechanism that translates experiences of sexualization at the
cultural level to psychological (e.g., anxiety, self-esteem,
authenticity, motivational states) and behavioral (cognitive
performance, body monitoring) features of mental health and well-being
at the individual level (Calogero, Tantleff-Dunn, \& Thompson, 2011;
Moradi \& Huang, 2008). Calogero et al. (2011) proposes that the
construct of self-objectification can be conceptualized as a learned
trait. Furthermore, it can also be elicited momentarily, through the
media, for example, with sexualized images in movies and magazines,
which can lead to a state of self-objectification (Calogero et al.,
2011, Moradi and Huang (2008)). Being objectified by another person and
possessing trait-level self-objectification (TSO) may interact to
influence experiences of feeling like a body, or state
self-objectification (SSO) (CITE swimsuit sweater, Garcia et al., 2016).
Does this habit self-objectification lead women to also objectify other
women, possibly to compare oneself?

@@

SIMO model and literature review (Gervais et al., 2020). Studies have
shown that within social encounters women are gazed at more than men
(Briton \& Hall, 1995, CITE saguy skype study, calogero video walking
study), often times feel \enquote{looked at} within interpersonal
interactions (Argyle \& Williams, 1969), and will more than likely
internalize the objectifying gaze on physical self (Young, 1979).
Moreover, perhaps the most adverse effect of objectifying treatment is
that it effectively socializes girls and women to treat themselves as
objects to be looked at and evaluated, an effect termed
self-objectification (Bartky, 1990; Berger, Cohen, \& Zelditch Jr, 1972;
L. Fredrickson, Roberts, M. Noll, Quinn, \& Twenge, 1998). We don't know
about women-on-women interpersonal objectification. What might be
different?

Self-objectification has been found to occur after a mere relationship
prime among women (Sanchez \& Broccoli, 2008) because in our culture
women need to look attractive to obtain and maintain successfuol
relationship, thus, the ``college relationships condition may highten
self-objectification and the evaluation of other women in a sexualized
way. Researchers have also studied interpersonal objectification and
self-objectification in romantic relationships (Strelan \& Pagoudis,
2018). Evidence is mixed, and women can sometimes have positive outcomes
from appearance valuation within the context of an established romantic
relationship and they experience less SSO after appearance comments
within romantic relationships (Meltzer, 2020), less is known about first
dates. But this literature is also only about heterosexual
relationships. A recent study has investigated the effect of
self-objectification on the reduction of relationship biulding skills in
general (including same-sex friendships) {[}CITE PWQ paper I reviewed,
Yoder editor{]}. Empirical evidence reveals that objectification
manifests through inauthenticity in romantic relationships (Brunell et
al., 2010), adverse attitudes in regard to career aspirations, and a
decrease in concentration and impairment in female cognitive performance
(D. M. Quinn, Chaudoir, \& Kallen, 2011).

MAYBE SEPARATE PARAGRAPH ABOUT AUTHENTICITY LINK SPECIFICALLY. And how
woman-woman interpersonal objectificaiton preocesses might diverge from
this process. {[}again CITE PWQ paper I reviewed, Yoder editor{]}.

@@

The decision was made to ask even heterosexual women to judge their
women partners as potential romantic partners. We felt that this prompt
would keep the study closest to a replication of the previous Garcia et
al. (2016) version of the study. Past research has found that women,
largely due to an increase self-objectifying state, are indeed able to
evaluate other women's potential as romantic partners--indeed, women may
be unfortunutely used to thinking this way about themselves, and we
suspect other women.

@@

To assess state self-objectification, we used an average of two items
from Saguy, Quinn, F Dovidio, and Pratto (2010) that were also used in
Garcia et al. (2016). Participants were asked to rank how much they
agreed with the following statements: \enquote{During the interaction I
felt more like a body than a full self} and \enquote{I felt more like a
body than as a real person in the interaction}. Originally, Saguy et al.
(2010) used 3 items, but in both samples the reliability of the scale
was higher once the third item was removed, so we chose to only use the
first two for our measure of SSO, leaving us with a reliable scale
(\(\alpha\) = 0.84 for Sample 1, and \(\alpha\) = 0.85 for Sample 2.)

@@

Trait self-objectification (TSO) was assessed using the
Self-Objectification Questionnaire (L. Fredrickson et al., 1998; M. Noll
\& L. Fredrickson, 1998), which evaluates the extent to which
individuals view their bodies in observable versus nonobservable ways.
The questionnaire asked participants to rank order both appearance and
functional aspects of their bodies, from 1 (least important) to 10 (most
important), with respect to physical self-concepts. Of the ten body
attributes, five of the items were appearance-based (weight, sex appeal,
physical attractiveness, firm/sculpted muscles and body measurements),
and five of the items were competence-based (strength, physical
coordination, energy level, health and physical fitness). Difference
scores were computed by subtracting the sum of the 5 functional
aspects/competence attributes (e.g., health, strength) from the sum of
the 5 physical self-concepts/appearance attributes (e.g., physical
attractiveness, weight), and all measures were multiplied by -1, as was
done in Garcia et al. (2016), so that positive scores indicated greater
TSO.

@@

This study sought to replicate the results of Garcia et al. (2016)'s
study, done with male-female pairs, which used a dyadic path analysis to
detect whether partners' objectification of one another affected state
self-objectification (SSO). See Figure~\ref{fig:2016figure} for the
results of the analysis from this previous study. We hope to investigate
how the central effects found in the previous study relate to
interactions between two women. Specifically, we are interested in
testing the relationship between state-other objectification and SSO,
and how SSO in turn, affecs feelings of inauthenticity during the
interaction. In addition, we will also test if the effect of
other-objectification in an interaction on SSO is only present for those
women who are high in trait self-objectification, as in Garcia et al.
(2016). Further, we will investigate the realtionships between
experiencing interaction inauthenticity and relationship agency, career
aspirations, and cognitive performance.

While Garcia et al. (2016) used dyadic path analysis, we will conduct
our dyadic analyses using multilevel modeling. Dyadic analyses for
distingishable dyads (e.g., mixed-gender interacting pairs) is more
natural in Structual Equation Modeling (SEM) than it is for
indistinguishable dayds (e.g., same-gender interacting pairs) (Garcia,
Kenny, \& Ledermann, 2015; Ledermann \& Kenny, 2017). One reason for
this asymmetry is that, due to the arbitrary distinctions made bewteen
\enquote{partner 1} and \enquote{partner 2} in indistinguishable dyads,
many estimates need to be fixed to be equal (i.e., paths, variances,
covariances, endogenous intercepts, and exogenous means) for
indistinguishable dyads but these equality contraints should not then be
considered in the degrees of freedom calculations for fit estimations
(Olsen \& Kenny, 2006). Further, Olsen and Kenny (2006) detail how a new
independence model and the corresponding fit measure should be
re-calculated for indistinguishable dyads models. The current study uses
dyadic multilevel modeling (MLM) to test all relationships and mediation
paterns. The online supplementary materials contains analysis using SEM.
See Ledermann and Kenny (2017) for a more complete discussion of the
considerations for using SEM versus MLM for dyadic analysis.

Testing the Garcia et al. (2016) model on the current, same-gender,
sample, involves using the Actor-Partner Independence Model (APIM)
approch for each outcome variable (i.e., endogenous variable in
Figure~\ref{fig:2016figure}). Thus, we ran five APIM's to test all the
hypothesized relationships. See Figure~\ref{fig:apim} for a basic APIM
model. The APIM includes effects due to one's own, as well as one's
partner's, predictor variables (\(X\)'s) on the one's own outcome
variable (\(Y\)). Unlike the original Garcia et al. (2016) study, our
study deals with indistinguishable dyads, meaning the designation of who
is designated as \enquote{actor} and who is designated as
\enquote{partner} is arbitrary. Recall that the indistinguiahble nature
of the dyads in the current study led us to choose the MLM approach over
SEM. These analyses are considered exploratory, given the lack of prior
research theorizing about these linkages.

@@

The correaltions between study variables is similar across samples. The
realibialities for the study scales were also equivalent. (Note that the
two samples were two small to conduct formal measurement equivalence
tests for scales.) There are no statistically significant differences
between samples in demographics including age, STATS, and ethnicity,
STATS.

@@

The most important finding from Garcia et al. (2016) was the significant
partner effect of other objectification and SSO (specifically men's
objectification of women and women's SSO). As expected, the partner
effect of other-objectification on SSO in the current all-women sample
was statistically signficant, \emph{b} = 0.29, \emph{SE} = 0.12,
\emph{p} = .019, replicating Garcia et al. (2016)'s fiding. One's own
other objectification had no effect on SSO, \emph{b} = -0.16, \emph{SE}
= 0.12, \emph{p} = .210. Contrary to past finding however, there was no
statistically significant interaction of partner's other objectification
and the person's trait self-objectification on SSO, \emph{b} = 0.03,
\emph{SE} = 0.27, \emph{p} = .910. There was also no significant main
effect of trait self-objectification on SSO \emph{b} = 0.07, \emph{SE} =
0.05, \emph{p} = .183.

Contrary to expectations, there was no significant effect of SSO on
interaction authenticity, although the estimate of this effect was in
the hypothesized negative direction, \emph{b} = -0.09, \emph{SE} = 0.12,
\emph{p} = .431. Because authenticity was a composite score of 9 items,
two of which were interaction specific authenticity items, we also
estimated the pairwise correlations bewteen SSO and all these items
individually. They were all small, ranging from only -0.01 to -0.14.
Although we hypothesized that SSO would mediate the relationship between
partner's other objectification and interaction authenticity, after
finding no relationship bewteen SSO and authencity, we also tested if
the partner's other objectification had a direct effect on authenticity,
but this effect was not significant, \emph{b} = 0.06, \emph{SE} = 0.12,
\emph{p} = .608 (nor was the total effect of partner's other
objectification on authenticity, \emph{b} = 0.03, \emph{SE} = 0.11,
\emph{p} = .787).

Lastly, althought there was no evidence that SSO was related to
interaction authenticity in the current sample, we tested if interaction
authenticity (composite of nine items) had effects on cognitive
performace, career aspirations, and relationship agency, as it did in
Garcia et al. (2016). We again used MLM and thus, these efefcts were
tested in three separate models. There was no significant effect of
interaction authenticity on cognitive performance, \emph{b} = 0.32,
\emph{SE} = 0.28, \emph{p} = .258, but authenticity was significantly
positively related to both career aspirations, \emph{b} = 0.18,
\emph{SE} = 0.07, \emph{p} = .010, and relationships agency, \emph{b} =
0.23, \emph{SE} = 0.12, \emph{p} = .049. There was no direct effect of
SSO on cognitive performance, \emph{b} = 0.04, \emph{SE} = 0.25,
\emph{p} = .872, and no direct effect of partner's other objectificaiton
on cognifitve performance, \emph{b} = 0.01, \emph{SE} = 0.27, \emph{p} =
.962. There was no direct effect of SSO on career aspirations, \emph{b}
= 0.03, \emph{SE} = 0.06, \emph{p} = .657, and no direct effect of
partner's other objectificaiton on career aspirations, \emph{b} = -0.06,
\emph{SE} = 0.07, \emph{p} = .378. There was no direct effect of SSO on
relationship agency, \emph{b} = -0.05, \emph{SE} = 0.11, \emph{p} =
.659, and no direct effect of partner's other objectificaiton on
relationship agency, \emph{b} = -0.1, \emph{SE} = 0.11, \emph{p} = .365.

@@

Sexism has recently been found to be related to the objectification of
women, but not men, for both men and women (Harsey \& Zurbriggen, 2020).
Empirical evidence illustrates how women continue to be objects of
interpersonal discrimination and expereince daily sexist hassles (Swim,
Hyers, Cohen, \& Ferguson, 2001). One form of interpersonal
discrimination women face is the process by which their whole being is
viewed as a collection of sexualized body parts valued predominantly for
commodification, a phenomena termed sexual objectification (Bartky,
1990). Sexual objectification occurs with both \enquote{endless variety
and monotonous similarity,} and is thus mediated by unique combinations
of race, ethnicity, sexuality, age, and class (Fredrickson, Hendler,
Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser and
Nicholson (1989), p.~28). Amid such heterogeneity though,
\enquote{having a reproductively mature female body} proposed by Roberts
and Fredrickson (1997) is likely to create a shared vulnerability to
sexual objectification and a variety of shared negative experiences as a
result.

@@

Also, future experiments or longitudinal studies should explore the
external validity of the notions of self-objectification and how the
operalization of self-objectification may be improved.

>>>>

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Objectification in Action: Self- and Other-Objectification in Same-gender Interactions},
            pdfauthor={Randi L. Garcia, Kat Kyuchukova, Asha Hinson, \& Lanee Jung},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Objectification in Action: Self- and Other-Objectification in
Same-gender Interactions}
    \author{Randi L. Garcia\textsuperscript{1, 2}, Kat
Kyuchukova\textsuperscript{1}, Asha Hinson\textsuperscript{1}, \& Lanee
Jung\textsuperscript{1}}
    \date{}

@@

Roberts and Fredrickson (1997) Objectification Theory, suggests that
women are objectified in interpersonal encounters, and that the effect
might be strongest from men, but possibly also from women. Psychological
researchers studying the sexual objectification of women, and the
resulting self-objectification that follows, have in recent years
explored the interpersonal process of the objectification -
self-objectification link. For example, in a face-to-face mixed-gender
dyadic study, Garcia, Earnshaw, and Quinn (2016) found that men's
reported objectification of their female interaction partner during an
interaction was associated with increased self-objectification reported
by their partner. Gervais, Sáez, Riemer, and Klein (2020) has reviewed
the literature on interpersonal self-objectification and has organized
the the process in a theoretical model called the SIMO, but this model
is only relevant for mixed-gender encounters. Although there is ample
evidence that women objectify other women (Loughnan et al., 2015a; Puvia
\& Vaes, 2013), there is currently no studies investigating the process
of interpersonal objectification same-gender interactions. Does
objectification by a female interaction partner have the same downstream
negative consequences as being objectified by a male interaction
partner? For example, perhaps women could be amplifying each others'
self-objectification as they get ready to go out for the night,
\emph{before} the theoretical encounters with men outlined in Gervais et
al. (2020) occur.

\subsection{Self-Objectification}\label{self-objectification}

Self-objectification is a multidimensional process that accounts for the
cognitive mechanism that translates experiences of sexualization at the
cultural level (Loughnan et al., 2015a) to psychological (e.g., anxiety,
self-esteem, authenticity, motivational states) and behavioral
(cognitive performance, body monitoring) features of mental health and
well-being at the individual level (Calogero, Tantleff-Dunn, \&
Thompson, 2011; Moradi \& Huang, 2008). Calogero et al. (2011) proposes
that the construct of self-objectification can be conceptualized as a
learned trait. Furthermore, it can also be elicited momentarily, through
the media, for example, with sexualized images in movies and magazines,
which can lead to a state of self-objectification (Bernard, Legrand, \&
Klein, 2018; Calogero et al., 2011; Moradi \& Huang, 2008). Being
objectified by another person and possessing trait-level
self-objectification (TSO) may interact to influence experiences of
feeling like a body, or state self-objectification (SSO) (B. L.
Fredrickson, Roberts, Noll, Quinn, \& Twenge, 1998, Garcia et al.
(2016)). Does this habit self-objectification lead women to also
objectify other women, possibly to compare oneself?

\subsection{Women Objectifying Women}\label{women-objectifying-women}

@@

\subsection{Interpersonal
Objectification}\label{interpersonal-objectification}

SIMO model and literature review (Gervais et al., 2020). Studies have
shown that within social encounters women are gazed at more than men
(Briton \& Hall, 1995), often times feel \enquote{looked at} within
interpersonal interactions (Argyle \& Williams, 1969; Miles-McLean et
al., 2015), and will more than likely internalize the objectifying gaze
on physical self (Puvia \& Vaes, 2013; Young, 1979). Moreover, perhaps
the most adverse effect of objectifying treatment is that it effectively
socializes girls and women to treat themselves as objects to be looked
at and evaluated, an effect termed self-objectification (Bartky, 1990;
Berger, Cohen, \& Zelditch Jr, 1972; B. L. Fredrickson et al., 1998). We
don't know about women-on-women interpersonal objectification. What
might be different?

Self-objectification has been found to occur after a mere relationship
prime among women (Sanchez \& Broccoli, 2008) because in our culture
women need to look attractive to obtain and maintain successful
relationship, thus, the ``college relationships condition may heighten
self-objectification and the evaluation of other women in a sexualized
way. Researchers have also studied interpersonal objectification and
self-objectification in romantic relationships (Strelan \& Pagoudis,
2018). Evidence is mixed, and women can sometimes have positive outcomes
from appearance valuation within the context of an established romantic
relationship and they experience less SSO after appearance comments
within romantic relationships (Meltzer, 2020), less is known about first
dates. But this literature is also only about heterosexual
relationships. A recent study has investigated the effect of
self-objectification on the reduction of relationship building skills in
general (including same-sex friendships) {[}CITE PWQ paper I reviewed,
Yoder editor{]}. Empirical evidence reveals that objectification
manifests through inauthenticity in romantic relationships (Brunell et
al., 2010), adverse attitudes in regard to career aspirations, and a
decrease in concentration and impairment in female cognitive performance
(Kahalon, Shnabel, \& Becker, 2018; D. M. Quinn, Chaudoir, \& Kallen,
2011). Both romantic relationships and relationships in general have
been studies in the context of objectification, but neither of these
literatures have investigated specifically same-gender relationships.

There is evidence that the experience of state self-objectification in
mixed-gender contexts (stranger and romantic) and within the self in any
moment (trying on a swimsuit) has negative consequences, but what about
in the context of interaction with other women? Is the
self-objectification experience in mixed-gender interactions the same as
that experienced in same-gender interactions? The ample research
demonstrating that the male gaze has a particularly detrimental effect
would suggest no (Gay \& Castano, 2010; Gervais, Vescio, \& Allen, 2011;
Saguy, Quinn, F Dovidio, \& Pratto, 2010, Calogero (2004)). Women do
objectify other women (Harsey \& Zurbriggen, 2020; Loughnan et al.,
2015a; Puvia \& Vaes, 2013), but when they do it, does it lead to
self-objectification in the same way men's objectification of women does
(Garcia et al., 2016)? If so, does the self-objectification experienced
in these same-gender interactions have the same negative consequences
for authenticity in that ineraction?

\subsection{Interpersonal Objectification and
Authenticity}\label{interpersonal-objectification-and-authenticity}

There is some evidence that reduced authenticity is a consequence of
self-objectification in the moment {[}Garcia et al. (2016); again CITE
PWQ paper I reviewed, Yoder editor{]}. This link has been justified by
the literature on stigmatized-stigmatizer interactions, viewing the
experience of being objectified in an interaction as an identity threat
situation. When a woman is objectified by a man, and then experiences
self-objectification, this intergroup encounter might trigger identitiy
threat, but is the same negative consequence present when a woman is
objectified by another woman? woman-woman interpersonal objectification
processes might diverge from this process. One the one hand, she may not
be having the same negative consequences the cascade from situations
that threated group-based identity (Deaux \& Major, 1987; Dovidio, Hebl,
Richeson, \& Shelton, 2006; M. R. Hebl \& Dovidio, 2005), but feeling
like a body, rather than a full human, in an interaction may be enough
to reduce feelings of authenticity and social competence, regardless of
the gender of the objectifyer {[}Tolman, Impett, Tracy, and Michael
(2006); PWQ paper I reviewed, Yoder editor{]}.

\subsection{The Current Study}\label{the-current-study}

@@

The decision was made to ask even heterosexual women to judge their
women partners as potential romantic partners. We felt that this prompt
would keep the study closest to a replication of the previous Garcia et
al. (2016) version of the study. Past research has found that women,
largely due to an increase self-objectifying state, are indeed able to
evaluate other women's potential as romantic partners--indeed, women may
be unfortunately used to thinking this way about themselves, and we
suspect other women.

@@

To assess state self-objectification, we used an average of two items
from Saguy et al. (2010) that were also used in Garcia et al. (2016).
Participants were asked to rank how much they agreed with the following
statements: \enquote{During the interaction I felt more like a body than
a full self} and \enquote{I felt more like a body than as a real person
in the interaction}. Originally, Saguy et al. (2010) used 3 items, but
in both samples the reliability of the scale was higher once the third
item was removed, so we chose to only use the first two for our measure
of SSO, leaving us with a reliable scale (\(\alpha\) = 0.84 for Sample
1, and \(\alpha\) = 0.85 for Sample 2.)

@@

Trait self-objectification (TSO) was assessed using the
Self-Objectification Questionnaire (B. L. Fredrickson et al., 1998; M.
Noll \& L. Fredrickson, 1998), which evaluates the extent to which
individuals view their bodies in observable versus non-observable ways.
The questionnaire asked participants to rank order both appearance and
functional aspects of their bodies, from 1 (least important) to 10 (most
important), with respect to physical self-concepts. Of the ten body
attributes, five of the items were appearance-based (weight, sex appeal,
physical attractiveness, firm/sculpted muscles and body measurements),
and five of the items were competence-based (strength, physical
coordination, energy level, health and physical fitness). Difference
scores were computed by subtracting the sum of the 5 functional
aspects/competence attributes (e.g., health, strength) from the sum of
the 5 physical self-concepts/appearance attributes (e.g., physical
attractiveness, weight), and all measures were multiplied by -1, as was
done in Garcia et al. (2016), so that positive scores indicated greater
TSO.

@@

This study sought to replicate the results of Garcia et al. (2016)'s
study, done with male-female pairs, which used a dyadic path analysis to
detect whether partners' objectification of one another affected state
self-objectification (SSO). See Figure~\ref{fig:2016figure} for the
results of the analysis from this previous study. We hope to investigate
how the central effects found in the previous study relate to
interactions between two women. Specifically, we are interested in
testing the relationship between state-other objectification and SSO,
and how SSO in turn, affects feelings of inauthenticity during the
interaction. In addition, we will also test if the effect of
other-objectification in an interaction on SSO is only present for those
women who are high in trait self-objectification, as in Garcia et al.
(2016). Further, we will investigate the relationships between
experiencing interaction inauthenticity and relationship agency, career
aspirations, and cognitive performance.

While Garcia et al. (2016) used dyadic path analysis, we will conduct
our dyadic analyses using multilevel modeling. Dyadic analyses for
distinguishable dyads (e.g., mixed-gender interacting pairs) is more
natural in Structural Equation Modeling (SEM) than it is for
indistinguishable dayds (e.g., same-gender interacting pairs) (Garcia,
Kenny, \& Ledermann, 2015; Ledermann \& Kenny, 2017). One reason for
this asymmetry is that, due to the arbitrary distinctions made between
\enquote{partner 1} and \enquote{partner 2} in indistinguishable dyads,
many estimates need to be fixed to be equal (i.e., paths, variances,
covariances, endogenous intercepts, and exogenous means) for
indistinguishable dyads but these equality constraints should not then
be considered in the degrees of freedom calculations for fit estimations
(Olsen \& Kenny, 2006). Further, Olsen and Kenny (2006) detail how a new
independence model and the corresponding fit measure should be
re-calculated for indistinguishable dyads models. The current study uses
dyadic multilevel modeling (MLM) to test all relationships and mediation
patterns. The online supplementary materials contains analysis using
SEM. See Ledermann and Kenny (2017) for a more complete discussion of
the considerations for using SEM versus MLM for dyadic analysis.

Testing the Garcia et al. (2016) model on the current, same-gender,
sample, involves using the Actor-Partner Independence Model (APIM)
approach for each outcome variable (i.e., endogenous variable in
Figure~\ref{fig:2016figure}). Thus, we ran five APIM's to test all the
hypothesized relationships. See Figure~\ref{fig:apim} for a basic APIM
model. The APIM includes effects due to one's own, as well as one's
partner's, predictor variables (\(X\)'s) on the one's own outcome
variable (\(Y\)). Unlike the original Garcia et al. (2016) study, our
study deals with indistinguishable dyads, meaning the designation of who
is designated as \enquote{actor} and who is designated as
\enquote{partner} is arbitrary. Recall that the indistinguishable nature
of the dyads in the current study led us to choose the MLM approach over
SEM. These analyses are considered exploratory, given the lack of prior
research theorizing about these linkages.

@@

The correlations between study variables is similar across samples. The
reliabilities for the study scales were also equivalent. (Note that the
two samples were two small to conduct formal measurement equivalence
tests for scales.) There are no statistically significant differences
between samples in demographics including age, STATS, and ethnicity,
STATS.

@@

The most important finding from Garcia et al. (2016) was the significant
partner effect of other objectification and SSO (specifically men's
objectification of women and women's SSO). As expected, the partner
effect of other-objectification on SSO in the current all-women sample
was statistically significant, \emph{b} = 0.29, \emph{SE} = 0.12,
\emph{p} = .019, replicating Garcia et al. (2016)'s finding. One's own
other objectification had no effect on SSO, \emph{b} = -0.16, \emph{SE}
= 0.12, \emph{p} = .210. Contrary to past finding however, there was no
statistically significant interaction of partner's other objectification
and the person's trait self-objectification on SSO, \emph{b} = 0.03,
\emph{SE} = 0.27, \emph{p} = .910. There was also no significant main
effect of trait self-objectification on SSO \emph{b} = 0.07, \emph{SE} =
0.05, \emph{p} = .183.

Contrary to expectations, there was no significant effect of SSO on
interaction authenticity, although the estimate of this effect was in
the hypothesized negative direction, \emph{b} = -0.09, \emph{SE} = 0.12,
\emph{p} = .431. Because authenticity was a composite score of 9 items,
two of which were interaction specific authenticity items, we also
estimated the pairwise correlations between SSO and all these items
individually. They were all small, ranging from only -0.01 to -0.14.
Although we hypothesized that SSO would mediate the relationship between
partner's other objectification and interaction authenticity, after
finding no relationship between SSO and authenticity, we also tested if
the partner's other objectification had a direct effect on authenticity,
but this effect was not significant, \emph{b} = 0.06, \emph{SE} = 0.12,
\emph{p} = .608 (nor was the total effect of partner's other
objectification on authenticity, \emph{b} = 0.03, \emph{SE} = 0.11,
\emph{p} = .787).

Lastly, although there was no evidence that SSO was related to
interaction authenticity in the current sample, we tested if interaction
authenticity (composite of nine items) had effects on cognitive
performance, career aspirations, and relationship agency, as it did in
Garcia et al. (2016). We again used MLM and thus, these effects were
tested in three separate models. There was no significant effect of
interaction authenticity on cognitive performance, \emph{b} = 0.32,
\emph{SE} = 0.28, \emph{p} = .258, but authenticity was significantly
positively related to both career aspirations, \emph{b} = 0.18,
\emph{SE} = 0.07, \emph{p} = .010, and relationships agency, \emph{b} =
0.23, \emph{SE} = 0.12, \emph{p} = .049. There was no direct effect of
SSO on cognitive performance, \emph{b} = 0.04, \emph{SE} = 0.25,
\emph{p} = .872, and no direct effect of partner's other objectification
on cognitive performance, \emph{b} = 0.01, \emph{SE} = 0.27, \emph{p} =
.962. There was no direct effect of SSO on career aspirations, \emph{b}
= 0.03, \emph{SE} = 0.06, \emph{p} = .657, and no direct effect of
partner's other objectification on career aspirations, \emph{b} = -0.06,
\emph{SE} = 0.07, \emph{p} = .378. There was no direct effect of SSO on
relationship agency, \emph{b} = -0.05, \emph{SE} = 0.11, \emph{p} =
.659, and no direct effect of partner's other objectification on
relationship agency, \emph{b} = -0.1, \emph{SE} = 0.11, \emph{p} = .365.

@@

Sexism has recently been found to be related to the objectification of
women, but not men, for both men and women (Harsey \& Zurbriggen, 2020).
Empirical evidence illustrates how women continue to be objects of
interpersonal discrimination and experience daily sexist hassles (Swim,
Hyers, Cohen, \& Ferguson, 2001). One form of interpersonal
discrimination women face is the process by which their whole being is
viewed as a collection of sexualized body parts valued predominantly for
commodification, a phenomena termed sexual objectification (Bartky,
1990). Sexual objectification occurs with both \enquote{endless variety
and monotonous similarity,} and is thus mediated by unique combinations
of race, ethnicity, sexuality, age, and class (Fredrickson, Hendler,
Nilsen, O'Barr, \& Roberts, 2011; Rubin, 1975, cited in Fraser and
Nicholson (1989), p.~28). Amid such heterogeneity though,
\enquote{having a reproductively mature female body} proposed by Roberts
and Fredrickson (1997) is likely to create a shared vulnerability to
sexual objectification and a variety of shared negative experiences as a
result.

@@

Also, future experiments or longitudinal studies should explore the
external validity of the notions of self-objectification and how the
operationalization of self-objectification may be improved.
